Corpus Analysis

### 2020-08-27 inst/analysis/corpus-stage2.Rmd
Fix missing package in cran-programs.fst

package_programs <-
  left_join(
    filter(package_runs, exitval==0) %>% select(package, file, dir, time), 
    runnable_code_raw %>% select(package, file=filename, code),
    by=c("package", "file")
  ) %>%
  filter(!endsWith(file, "tests/testthat.R"), !endsWith(file, "tests/run-all.R")) %>% # testthat drivers are not traced
  transmute(
    type=basename(dirname(file)),
    file=as.character(path(dir, "calls.fst")),
    code, 
    runtime=time,
    corpus="cran"
  )

>>>>

package_programs <-
  left_join(
    filter(package_runs, exitval==0) %>% select(package, file, dir, time), 
    runnable_code_raw %>% select(package, file=filename, code),
    by=c("package", "file")
  ) %>%
  filter(!endsWith(file, "tests/testthat.R"), !endsWith(file, "tests/run-all.R")) %>% # testthat drivers are not traced
  transmute(
    package,
    type=basename(dirname(file)),
    file=as.character(path(dir, "calls.fst")),
    code, 
    runtime=time,
    corpus="cran"
  )
